### 2018-05-05 papers/synth/prelim.tex
asd

The following constraints encode the basic consistency of VTSs.
\begin{align*}
  \texttt{EdgeC} =\;& \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
  \land
  \bigwedge\limits_{i,q} \neg e_{i,i,q}
  \land
  % \tag{\texttt{NodeC}}\label{eq:f0}\\
  \bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
  \\
  \texttt{ActivityC} =\;&
  \bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
  % \tag{V2}\label{eq:f1}\\
  \\
  \texttt{PairingC} =\;&
  \exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
                         (p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
% \land\\ 
%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
  % \bigwedge\limits_{m} 
  % (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
  % (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
  \\
  \texttt{Fusion1} =\;&
  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
  \bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
                        \Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
  & \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
  \\
  \texttt{Fusion2} =\;&
\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \neg 
  \bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land .. \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
  \\
  \texttt{Consistancy} =\;& \texttt{EdgeC} \land
  \texttt{ActivityC} \land \texttt{PairingC} \land
  \texttt{Fusion1} \land \texttt{Fusion2} 
\end{align*}
\texttt{EdgeC} states that each edge has at least one molecule,
there are no self loops, and edge labels are consistent with node labels.   
\texttt{ActivityC} states that active molecule are present.
\texttt{PairingC} states that a molecule can either participate in fusion
via nodes or via edges, but not both.
\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
\texttt{Consistancy} is the conjunction of all of the above.

@@

\paragraph{$k$-connected property}
%
$k$-connectedness expresses robustness against failure of few edges.
%
Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
the modified VTS.
%
% To check whether $k$-connected is a
% necessary condition, we remove (drop) $k-1$ edges from the graph and
% if it disconnects the graph, and we get an assignment.
% %
% We have a graph that is not $k$-connected.
%
In the following, $\texttt{Fail}(d,k)$ encodes that only
existing edges can be failed and exactly $k-1$ edges are failed.
%
$\texttt{FailReach}(d,r')$ defines reachability in the modified VTS.
%
We use a new variable $r'_{i,j,p}$ to encode reachability from
$i$ to $j$ in at most $p$ steps.
%
$\texttt{Connected}(r')$ says that all nodes are reachable from any
other node.
\begin{align*}
  \texttt{Fail}(d,k) = & 
  \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
  \sum_{i,j,q} d_{i,j,q} = k-1\\
  % \texttt{ReachAbove}(d,r') = &
  % \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
  \texttt{FailReach}(d,r') = &
   \bigwedge\limits_{i,j,p}  r^{\prime}_{i,j,p} \limplies [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
  \texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
\end{align*}
We will be synthesizing $k$-connected graphs.
%
We define $\texttt{Connected}(k)$ that says for all possible valid failures
the graph remains reachable. 
\begin{align*}
  \texttt{Connected}(k) = & \forall d.\;
          (\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FailReach}(d,r')
                                \land \texttt{Connected}(r'))
% \\
  % \texttt{Disconnected}(k) = & \exists d.\;
  %         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
  %                               \land \lnot \texttt{Connected}(r'))
\end{align*}
Since $d$ variables in $\texttt{Connected}(k)$ are universally
quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
%

>>>>

The following constraints encode the basic consistency of VTSs.
\begin{align*}
  \texttt{EdgeC} =\;&\hspace{-1ex}\bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
  \land
  \bigwedge\limits_{i,q} \neg e_{i,i,q}
  \land
  % \tag{\texttt{NodeC}}\label{eq:f0}\\
  \bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
  \\
  \texttt{ActivityC} =\;&
  \bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
  % \tag{V2}\label{eq:f1}\\
  \\
  \texttt{PairingC} =\;&
  \exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
                         (p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
% \land\\ 
%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
  % \bigwedge\limits_{m} 
  % (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
  % (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
  \\
  \texttt{Fusion1} =\;&
  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
  \bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
                        \Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
  & \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
  \\
  \texttt{Fusion2} =\;&
\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
  & \hspace{2cm} \neg 
  \bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land .. \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
  \\
  \texttt{Consistancy} =\;& \texttt{EdgeC} \land
  \texttt{ActivityC} \land \texttt{PairingC} \land
  \texttt{Fusion1} \land \texttt{Fusion2} 
\end{align*}
\texttt{EdgeC} states that each edge has at least one molecule,
there are no self loops, and edge labels are consistent with node labels.   
\texttt{ActivityC} states that active molecule are present.
\texttt{PairingC} states that all molecules are divided into
two types and any fusing set of molecules
must have three molecules involved from one type and one molecule from the other.
\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
\texttt{Consistancy} is the conjunction of all of the above.

@@

\paragraph{$k$-connected property}
%
$k$-connectedness expresses robustness against failure of few edges.
%
Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
the modified VTS.
%
% To check whether $k$-connected is a
% necessary condition, we remove (drop) $k-1$ edges from the graph and
% if it disconnects the graph, and we get an assignment.
% %
% We have a graph that is not $k$-connected.
%
In the following, $\texttt{Fail}(d,k)$ encodes that only
existing edges can be failed and exactly $k-1$ edges are failed.
%
$\texttt{FReach}(d,r')$ defines reachability in the modified VTS.
%
We use a new variable $r'_{i,j,p}$ to encode reachability from
$i$ to $j$ in at most $p$ steps.
%
$\texttt{Connected}(r')$ says that all nodes are reachable from any
other node.
\begin{align*}
  \texttt{Fail}(d,k) = & 
  \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
  \sum_{i,j,q} d_{i,j,q} = k-1\\
  % \texttt{ReachAbove}(d,r') = &
  % \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
  \texttt{FReach}(d,r') = &\hspace{-1ex}
   \bigwedge\limits_{i,j,p}  \hspace{-1ex}r^{\prime}_{i,j,p} \hspace{-1ex}\limplies\hspace{-1ex} [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \hspace{-1pt}\lor \hspace{-2pt} (\bigvee_{\mathclap{i' \neq i}}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
  \texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
\end{align*}
We will be synthesizing $k$-connected graphs.
%
We define $\texttt{Connected}(k)$ that says for all possible valid failures
the graph remains reachable. 
\begin{align*}
  \texttt{Connected}(k) = & \forall d.\;
          (\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FReach}(d,r')
                                \land \texttt{Connected}(r'))
% \\
  % \texttt{Disconnected}(k) = & \exists d.\;
  %         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
  %                               \land \lnot \texttt{Connected}(r'))
\end{align*}
Since $d$ variables in $\texttt{Connected}(k)$ are universally
quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
%
